Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-04 paper.qmd
Updated Figure 2

data_two_curvy <- training_data_two_curvy_not_std |>
  mutate(type = "data")

@@

two_curvy_proj_umap_first_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.12, 0.12)) + 
  ylim(c(-0.12, 0.12)) +
  interior_annotation("c", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_first_model1_temp <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.1, 0.1)) + 
  ylim(c(-0.1, 0.1)) +
  interior_annotation("c2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| label: two-curvy-true-proj
# Apply the scaling
df_model_data_two_curvy <- bind_rows(data_two_curvy, true_model_two_curvy)

>>>>

data_two_curvy <- training_data_two_curvy |>
  mutate(type = "data")

data_two_curvy_not_std <- training_data_two_curvy_not_std |>
  mutate(type = "data")

@@

two_curvy_proj_umap_first_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.25, 0.25)) + 
  ylim(c(-0.25, 0.25)) +
  interior_annotation("c", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

two_curvy_proj_umap_first_model1_temp <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") + #31a354
  geom_point(
    size = 0.5,
    alpha = 0.2,
    color = "#636363") +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 4) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.25, 0.25)) + 
  ylim(c(-0.25, 0.25)) +
  interior_annotation("c2", sc_ltr_pos) +
  theme(
    legend.position = "none"
  )

@@

```{r}
#| label: two-curvy-true-proj
# Apply the scaling
df_model_data_two_curvy <- bind_rows(data_two_curvy_not_std, true_model_two_curvy)
